Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Minor changes with regard to parentheses to Sophos. References #31

With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users. But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad (even not on purpose) users' behaviour. Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs. Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately. Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach. For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe might be the chosen option. Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.

>>>>

With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users. But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even if it was not on purpose. Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs. Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately. Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach. For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe might be the chosen option. Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.
